Supplement to Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-02-20 supplement.tex
I updated the airmass analysis where I have not applied a linear de-trend to the time series. Now the time series at 1.38um very clearly correlates with airmass, almost perfectly.
I added a backup of the original BD amplitude spectra since I replaced the plots.

\clearpage
\section{Airmass Correlation}
One thing to check is that the U shaped light curves near the telluric water bands are correlated to airmass.
As I start, I took a time series at 1.26~$\mu$m to remove find a trend-line for brown dwarf modulations.
This is shown in Figure \ref{fig:1p26umFluxTrendFit}.
I then remove this polynomial trend from the 1.38~$\mu$m time series to remove the brown dwarf oscillations from it.
The residual light curve has a U shape similar to the airmass trend shown in Figure \ref{fig:1p38residAndAirmass}.
A direct correlation plot is shown in Figure \ref{fig:residAirmass1p38corr}.

@@

>>>>

\clearpage
\section{Airmass Correlation}
One thing to check is that the U shaped light curves near the telluric water bands are correlated to airmass.
As I start, I took a time series at 1.26~$\mu$m to remove find a trend-line for brown dwarf modulations and any other tends.
This is shown in Figure \ref{fig:1p26umFluxTrendFit}.
I then remove this polynomial trend from the 1.38~$\mu$m time series to remove the brown dwarf oscillations from it.
The residual light curve has a U shape similar to the airmass trend shown in Figure \ref{fig:1p38residAndAirmass}.
A direct correlation plot is shown in Figure \ref{fig:residAirmass1p38corr}.

@@

\clearpage
\section{Original Plots for reference}
\begin{figure*}
\centering
\subfloat[2MASS J0835 - \colorbox{red}{fit might need more work} ]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
	\label{fig:ampspec0835}
	}
\subfloat[2MASS J1821]{
	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
	\label{fig:ampspec1821}
	}
	\caption{Sine fit amplitude versus wavelength for each brown dwarf. The regions at 1.4~$\mu$m and 1.9~$\mu$m (shaded with a salmon color) are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star. 2MASS J0835 shows no clear trend in wavelength, while 2MASS J1821 has a strong slope indicative of Mie-scattering particles.}
	\label{fig:ampSpec}
\end{figure*}
